Helmet Foam Case Study Report

### 2024-04-29 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd

\begin{center}
\begin{tabular}{|l|l|}
\hline
\text{Variable Name} & \text{Description} \\
\hline
ID & the unique identifier of the different foam pieces \\
chemIndex & the chemical makeup type of the foam. 1 = 79, 2 = 100, 3 = 121 \\
porosity & the porosity level of the foam. Low = 71\%, high = 81\% \\
freq & the number of compressions per second (hz) \\
amp & the amplitude of the compressions \\
initialStrain & the initial measure of the strain of foam. (Originally labeled ``strain'') \\
initialStress & the initial measure of the stress of the foam. (Originally labeled ``stresskpa'') \\
cycle & the cycle number the measurement was taken at \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|}
\hline
\text{Variable Name} & \text{Description} \\
\hline
stiffness & measurement of the foam’s stiffness. (Originally labeled ``E1\_MPA'') \\
damping & measurement of the foam’s damping. (Originally labeled ``delta\_rad'') \\
stiffnessFrac & stiffness / first stiffness measurement \\
dampingFrac & tan(damping) / tan(first damping measurement) \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Variable Name} & \textbf{Description} \\
\hline
ID & The unique identifier of the different foam pieces \\
chemIndex & The chemical makeup type of the foam. 1 = 79, 2 = 100, 3 = 121 \\
porosity & The porosity level of the foam. Low = 71\%, high = 81\% \\
freq & The number of compressions per second (hz) \\
amp & The amplitude of the compressions \\
initialStrain & The initial measure of the strain of foam. (Originally labeled ``strain'') \\
initialStress & The initial measure of the stress of the foam. (Originally labeled ``stresskpa'') \\
cycle & The cycle number the measurement was taken at \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Variable Name} & \textbf{Description} \\
\hline
stiffness & Measurement of the foam’s stiffness. (Originally labeled ``E1\_MPA'') \\
damping & Measurement of the foam’s damping. (Originally labeled ``delta\_rad'') \\
stiffnessFrac & Stiffness / first stiffness measurement \\
dampingFrac & tan(damping) / tan(first damping measurement) \\
\hline
\end{tabular}
\end{center}
